~\\[1in] % hack to put space at top.
\textbf{\Huge Acknowledgments}\\

\noindent 
First and foremost, I would like to thank my advisor, Gail Kaiser, who has provided me invaluable guidance and wisdom in all matters related to my research and publishing. I truly appreciate the support, and am thankful for the flexibility and patience over the years in providing guidance in my research efforts.
\\ \\
I would also like to thank Franjo Ivancic, who has been a constant source of support and provided valuable feedback to my half-baked ideas.
A special thank you to Jonathan Bell, who provided insightful critique, and ideas which helped in re-shaping and significantly improving the work presented in this thesis. I would also like to thank Swapneel Sheth, and Chris Murphy who provided valuable support in terms of direction and practical experience during my initial years of the PhD.
\\ \\
The work described here has been supported by the Programming Systems Laboratory, and several members and associates of the PSL lab. 
I would like to thank Mike Su, Leon Wu, Simha Sethumadhavan, Ravindra Babu Ganapathi, and Jonathan Demme, and many others whom I had the pleasure to work with. I also had the pleasure of supervising a number of graduate students who have helped in testing out several early stage prototypes of different projects I was involved in.
\\ \\
I would also like to acknowledge my co-workers at NEC Labs America, I have had the pleasure to work with several extremely intelligent academicians, and have gained a lot from my experience in working with them. In particular I would like to thank - Hui Zhang, Junghwan Rhee, Cristian Lumezanu, Abhishek Sharma, Vishal Singh, Qiang Xu and several interns. I would also like to thank Kai Ma for his work towards the implementation of \emph{FPerf}, an application of \iprobe. 
\\ \\
Last but most important, I would like to thank my wife, my parents and my sister for sticking with me, and their emotional support and encouragement.
