\section{Implementation}
\label{sec:Implementation}

The design of iProbe is generic and platform agnostic, and works on native binary executables. 
We built a prototype on Linux which is a commonly used platform for service environments. 
In particular, we used a compiler technique based gcc/g++ compiler to implement the hook place holders on standard Linux 32 bit and 64 bit architectures. 
In this section we first show the implementation of the iProbe framework, and then discuss the implementation of FPerf a tool built using iProbe.

\subsection{iProbe Framework}
As we presented in the previous section, the instrumentation procedure consists of two stages.

\indent \textbf{ColdPatch}: In the first phase the place holders for hooks are created in the target binary. 
We implemented this by compiling binaries using the \texttt{-finstrument-functions} flag. 
Note that this can be done simply by appending this flag to the list of compiler flags (e.g., \texttt{CFLAG, CCFLAG, CXXFLAGS}) and most of cases it works without interfering with user code. 

%In details this compiler option places function calls to instrumentation functions (\texttt{\_cyg\_profile\_func\_enter} and \texttt{\_cyg\_profile\_func\_exit})  after the entry and before the exit of every function.
In details this compiler option places function calls to instrumentation functions after the entry and before the exit of every function.
This includes inline functions (see second state in Figure \ref{fig:state_rep}). 
Subsequently, our ColdPatcher uses a binary parser to read through all the target binaries, and search and replace the instruction offsets containing the instrumentation calls with NOP instructions (instruction 90). 
Symbolic and debug information is read from the target binary using commonly available \texttt{objdmp} tools; 
This information combined with target instruction offsets are used to generate the probe list with the following information:
\begin{verbatim}
<Instr Offset, Entry\Exit Point, Meta-Data>
\end{verbatim}
The first field is the instruction offset from the base address, and the second classifies if the target is an entry or an exit point of the function. 
The meta-data here specifies the file, function name, line number etc. 

\indent \textbf{HotPatching}: 
In the run-time phase, we first use the library interposition technique, \texttt{LD\_PRELOAD}, to preload the instrumentation functions in the form of a shared library to the execution environment. 
The HotPatcher then uses a command line interface which interacts with the user and provides the user an option to input the target process and the probe list.
Next, iProbe collects the base addresses of each shared library and the binary connected to the target process from \texttt{/proc/pid/maps}.
The load address and offsets from the probe-list are then used to generate a hash of all possible probing points. 
iProbe then use the meta-data information to provide users a list of target functions and their respective file information.  
It takes as input the list of targets and interrupts the target process. 
We then use \texttt{ptrace} functionality to patch the target instructions with calls to our instrumentation functions, and release the process to execute as normal.
The instrumentation from each function is registered and logged by a shared memory logger. 
To avoid any locking overhead, we have a race free mechanism which
utilizes thread local storage to keep all logs, and a buffered logging mechanism.

\input{iprobe/fperf}
